|

### 2019-06-05 inst/manuscript/manuscript.Rmd
Remove .docx output option from manuscript.Rmd
Also:
 - Remove associated components with .docx output

---
title: | 
   **Defining protein markers for *Candida albicans* extracellular vesicles**
author: | 
   *Charlotte Dawson^a^, Mark Bleackley^a^, Donovan Garcia Ceron^a^, 
   Marilyn Anderson^a^*
date: | 
   *^a^Department of Biochemistry and Genetics, La Trobe Institute for 
   Molecular Science, La Trobe University, Victoria, 3086, Australia*
output: 
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
    bookdown::word_document2:
      pandoc_args:
        '--lua-filter=components/pagebreak.lua'
      reference_docx: "components/draft_template.docx"
      fig_caption: yes
bibliography: "components/references.bib" 
csl: "components/molecular-and-cellular-proteomics.csl"
link-citations: yes
linkcolor: black
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \usepackage{lipsum}
  - \pagestyle{fancy}
  - \fancyhead[L]{This is the running title it is rather long}
  - \setlength{\headheight}{15pt}
  - \usepackage{float}
  - \let\origfigure\figure
  - \let\endorigfigure\endfigure
  - \renewenvironment{figure}[1][2]{\expandafter\origfigure\expandafter[H]}
    {\endorigfigure}
  - \usepackage{caption}
  - \captionsetup{font={normalsize,stretch=1.3},labelfont=bf}
  - \usepackage{threeparttable}
---

>>>>

---
title: | 
   **Defining protein markers for *Candida albicans* extracellular vesicles**
author: | 
   *Charlotte Dawson^a^, Mark Bleackley^a^, Donovan Garcia Ceron^a^, 
   Marilyn Anderson^a^*
date: | 
   *^a^Department of Biochemistry and Genetics, La Trobe Institute for 
   Molecular Science, La Trobe University, Victoria, 3086, Australia*
output: 
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
bibliography: "components/references.bib" 
csl: "components/molecular-and-cellular-proteomics.csl"
link-citations: yes
linkcolor: black
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \usepackage{lipsum}
  - \pagestyle{fancy}
  - \fancyhead[L]{This is the running title it is rather long}
  - \setlength{\headheight}{15pt}
  - \usepackage{float}
  - \let\origfigure\figure
  - \let\endorigfigure\endfigure
  - \renewenvironment{figure}[1][2]{\expandafter\origfigure\expandafter[H]}
    {\endorigfigure}
  - \usepackage{caption}
  - \captionsetup{font={normalsize,stretch=1.3},labelfont=bf}
  - \usepackage{threeparttable}
---
